### 2014-04-16 doc/uist14/iteration3.tex
iteration 3: further gender neutraility

In the first stage, the user orients his head towards each device, and the system saves the absolute orientations of each device. Once the user has added all devices, these orientations are saved for future use. It is still possible to add new devices at any point without running the entire calibration step, as the system will simply store the absolute orientation of the new device.

During the second stage, when the user wants to use his head-motion for disambiguation, they will put their finger on the touchpad to enter a quasi-mode.  This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.

>>>>

In the first stage, the user orients their head towards each device, and the system saves the absolute orientations of each device. Once the user has added all devices, these orientations are saved for future use. It is still possible to add new devices at any point without running the entire calibration step, as the system will simply store the absolute orientation of the new device.

During the second stage, when the user wants to use head-motion for disambiguation, they will put their finger on the touchpad to enter a quasi-mode.  This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.
